MP MetaAnalysis

### 2018-12-04 Paper_Analyses.Rmd
Latest comments

[Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]
[Christina: Works for me. I am just thinking what the Vihman-style framework says. do you happen to know? I think the Renner thesis discusses it.]
[Katie: I wasn't really familiar with the Vihman framework, but looking at Renner's thesis and some of the original papers suggests that it really is about production, not perception.]

@@

[Christina: I needed to move this around because we first need to say that we could not compute some effect sizes and removed outlierts.]

@@

[Katie] Do you want number of records and papers for the imputed correlations as well? You've put a -1, assuming there was something wrong with one of the papers or something like that? How does that shake out for number of records?
[Christina: No clue what the -1 was, sorry.]

@@

[Christina: In the above 2 paragraphs I got confused, should it be present or past. I think it switched in the las tparagraph so I started to adapt, but I think it would be best for you to decide. ]
[Katie: Good catch. I've gone through the Methods section and changed everything to past, per APA guidelines.]

@@

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`. The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`). However, the lower bound of the CI is close to zero and considering the small sample size, one might hypothesize that with more power the small relationship might become even larger. As a result, we can draw a tentative conclusion that there is a positive relationship between comprehension scores and object recognition in response to correct pronunciations.

[Christina] It's significant now!
[Katie] Must be because you removed the outliers. I've changed around the wording :)

@@

We next considered the relationship between vocabulary and object recognition for mispronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`. The mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`). The small correlation and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations. We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.

Figure 4 plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis. This figure illustrates two things: the growing number of mispronunciation sensitivity studies and the waning number of studies measuring vocabulary. The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design. This may explain our underpowered analysis of the relationship between mispronunciation sensitivity and vocabulary size.

@@

In a typical trial in a mispronunciation sensitivity study, the target-distractor image pairs are first presented in silence, followed by auditory presentation of a carrier phrase or isolated presentation of the target word (correctly pronounced or mispronounced). When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. To examine the size of the time window analyzed in the post-naming phase, we must first consider overall length of time post-naming, because it limits the overall time window available to analyze and might thus predict which time window was analyzed. Across papers, actual post-naming phase length varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms. We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions. There was an inverse relationship between infant age and actual post-naming phase length, such that younger infants were presented with longer a longer post-naming phase, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`). Presumably, younger infants may be exposed to longer trials because their word recognition abilities are expected to be slower than older infants (Fernald et al., 1998).

Unlike the actual post-naming phase length, the size of the post-naming time window analyzed can be chosen after the experimental data is collected. Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`). Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions. Similar to actual post-naming phase length, there was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`). Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998). To summarize, we observe variation in time-related aspects related to infants' age. This variation is most pronounced, and even significant, for the time window that is being analyzed after the target label has been heard.

@@

Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman, A., & Loken, E. (2013). Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.

@@

We first assessed whether size of the post-naming time window analyzed had an impact on the overall size of the reported mispronunciation sensitivity. We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`. The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`. This relationship is plotted in Figure 3a. The results suggest that the size of the post-naming phase analyzed significantly impacted mispronunciation sensitivity. Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.

Considering that we also found a relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the development of mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`. The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`. As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in mispronunciation sensitivity with development. For example, when experimental conditions were analyzed with a post-naming time window of 2000 ms or less, mispronunciation sensitivity is found to increase with infant age. If the post-naming time window analyzed is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age. In other words, all three possible hypotheses might be supported depending on analysis choices made regarding the size of the post-naming time window to analyze. This is especially important, considering that our key question is how mispronunciation sensitivity changes with development. These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming time window analyzed.

@@

We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity. When we included both condition and offset time as moderators, the moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`. Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the development of mispronunciation sensitivity. When both offset time and condition were included as moderators, the moderator test was significant `r mod_test(rma_offset_AGE_MS)`, but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`. Taken together, these results suggest that offset time does not modulate mispronunciation sensitivity. There is no relationship between offset time and age, and we find no influence of offset time on the development of mispronunciation sensitivity.

@@

The Difference Score and Pre vs. Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences. The Post dependent variable, in contrast, does not consider pre-naming preferences. To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of mispronunciation sensitivity, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis. We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations. Considering that the dependent variable Post differs in its consideration of pre-naming preferences, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs. Post dependent variables.

@@

@@

Overall, infants showed reliable correct object recognition when given both correctly pronounced and mispronounced labels. In other words, not only did infants correctly recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets. Mispronounced labels were considered a better match for target images than a distractor image, despite the differences in the phonological form of correctly pronounced and mispronounced words. Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting overall mispronunciation sensitivity in the current experimental literature.

We next evaluated the developmental trajectory of infants' mispronunciation sensitivity. Based on previous theoretical accounts and existing experimental evidence, we envisioned three possible developmental patterns: increasing sensitivity, decreasing sensitivity, and unchanging sensitivity. We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity. Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) account for a lack of developmental change. The results of our meta-analysis are supported by a handful of studies directly comparing infants over a range of ages (Swingley & Aslin, 2000; Bailey & Plunkett, 2002; Zesiger et al., 2012), which also found no developmental change in mispronunciation sensitivity.

Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general. Vocabulary growth leads to an increase (PRIMIR; Curtin & Werker, 2007; Werker & Curtin, 2005) or decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation sensitivity and vocabulary is expected to grow considerably in the age range considered in the current meta-analysis (see wordbank.stanford.edu; Frank et al., 2017). The lack of developmental effects found in the meta-analysis may therefore be due to using age, instead of vocabulary growth, as a facilitator for change in mispronunciation sensitivity. Yet, an analysis of correlations between vocabulary size and object recognition effect sizes does not support this argument. Although an increasing vocabulary size lead to increased object recognition for correctly pronounced words, this was not the case for mispronunciations. Some previous experimental evidence also supports a lack of a relationship between vocabulary size and mispronunciation sensitivity (e.g. Mani & Plunkett, 2007; Swingley &
Aslin, 2000; but see Mani & Plunkett, 2010). This would suggest that object recognition for mispronunciations is not modulated by vocabulary size, contrary to the predictions of the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts and further supporting the overall lack of an influence of age on mispronunciation sensitivity.

@@

Although the lack of an relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis. Despite the theoretical implications, less than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total). We suggest that this may be the result of publication bias, specifically a desire to not publish null results. Although the number of mispronunciation sensitivity studies has experience growth, this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.

@@

Then talk about the experimental decisions

** Data Analysis Choices **

  + Post-naming time window size and dependent variable impact misp sensitivity development
  + Offset time does not impact misp sensitivity development
  + the first two do not have theoretical frameworks to guide researchers, whereas offset time does

  [Christina] Did I ask the following already: Do we know whether subtrations were on the trial level? Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level. 
[Katie] You did. I'll put here my answer from before:
From working with Nivi, we did it participants x condition or participants x trial (but mostly the former). But, this is not something we reported in papers. I don't think I read it at all when putting together the dataset for this either.
[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)

When it comes to designing studies, best practices and current standards might not always overlap. Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press). A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework. Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere. We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation). Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.

@@

>>>>

@@

@@

@@

@@

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`. The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`). As a result, we can draw a tentative conclusion that there is a positive relationship between comprehension scores and object recognition in response to correct pronunciations.

@@

We next considered the relationship between vocabulary and object recognition for mispronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`. The mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`). The small correlation suggests a lack of relationship between vocabulary and object recognition for mispronunciations. We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.

Figure 4 plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis. This figure illustrates two things: the growing number of mispronunciation sensitivity studies and the waning number of studies measuring vocabulary. The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design. This may explain our underpowered analysis of the relationship between mispronunciation sensitivity and vocabulary size.

@@

In a typical trial in a mispronunciation sensitivity study, the target-distractor image pairs are first presented in silence, followed by auditory presentation of a carrier phrase or isolated presentation of the target word (correctly pronounced or mispronounced). When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. To examine the size of the time window analyzed in the post-naming phase, we must first consider overall length of time post-naming, because it limits the overall time window available to analyze and might thus predict which time window was analyzed. Across papers, actual post-naming phase length varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms. We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions. There was no apparent relation between infant age and overall post-naming phase duration (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).

[Christina: this r is near 0. I wouldn't interpret this as positive relationship, so I changed the wording here and in the next paragraph. Btw, can you add confidence intervals for r? The info is in there, with `$conf.int[1]`  and `$conf.int[2]`]

Unlike the actual post-naming phase length, the size of the post-naming time window analyzed can be chosen after the experimental data is collected. Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming phase, usually excluding later portions (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`). Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions. There was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`). The choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998). To summarize, we observe variation in time-related aspects related to infants' age.

[Christina: Below there is a .... Just so we don't forget it.]

@@

Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman & Loken, 2013). Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.

@@

[Christina: There are some () missing in the following paragraphs, I am a bit tired now, can you check?]

We first assessed whether size of the post-naming time window analyzed had an impact on the overall size of the reported mispronunciation sensitivity. We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`. The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`. This relationship is plotted in Figure 3a. The results suggest that the size of the post-naming phase analyzed significantly impacted mispronunciation sensitivity. Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase was shorter.

Considering that we found a significant relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the estimated size of mispronunciation sensitivity. We therefore included age as additional moderator of the previous analysis. The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`. The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`). As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in mispronunciation sensitivity with development. For example, when experimental conditions were analyzed with a post-naming time window of 2000 ms or less, mispronunciation sensitivity is found to increase with infant age. If the post-naming time window analyzed is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age. In other words, all three possible hypotheses might be supported depending on analysis choices made regarding the size of the post-naming time window to analyze. This is especially important, considering that our key question is how mispronunciation sensitivity changes with development. These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming time window analyzed.

@@

We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity. When we included both condition and offset time as moderators, the moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`. Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the development of mispronunciation sensitivity. When both offset time and condition were included as moderators, the moderator test was significant `r mod_test(rma_offset_AGE_MS)`, but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`. Taken together, these results suggest that offset time does not modulate mispronunciation sensitivity. There is no relationship between offset time and age, and we find no influence of offset time on the estimated size of mispronunciation sensitivity over age.

[Christina: Replaced development in the sentence above and earlier, because the analysis choice cannot affect the development, just our measure of it]

@@

The Difference Score and Pre vs. Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences. [Christina: adding sth here]. It should be noted, however, that the Difference Score can better counter act participant- and item-level differences, whereas Pre vs. Post is a group-level measure. The Post dependent variable, in contrast, does not consider pre-naming preferences. To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of mispronunciation sensitivity, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis. We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations. Considering that the dependent variable Post differs in its consideration of pre-naming preferences, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs. Post dependent variables.

@@

[Christina: Do you want to add this section?]

@@

Overall, infants showed reliable object recognition when given both correctly pronounced and mispronounced labels. In other words, not only did infants recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets. Mispronounced labels were considered a better match for target images than a distractor image, despite the differences in the phonological form of correctly pronounced and mispronounced words. Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting overall mispronunciation sensitivity in the current experimental literature. In short, infants show knowledge of what constitutes unacceptable variation in word forms, displaying knowledge of the role of phonemic changes throughout the ages assessed here. At the same time, infants, like adults, can recover from mispronunciations.

We next evaluated the developmental trajectory of infants' mispronunciation sensitivity. Based on previous theoretical accounts and existing experimental evidence, we envisioned three possible developmental patterns: increasing, decreasing, and unchanging sensitivity. We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity. Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) account for a lack of developmental change. The results of our meta-analysis are supported by a handful of studies directly comparing infants over a range of ages (Swingley & Aslin, 2000; Bailey & Plunkett, 2002; Zesiger et al., 2012), which also found no developmental change in mispronunciation sensitivity.

Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general. Vocabulary growth leads to an increase (PRIMIR; Curtin & Werker, 2007; Werker & Curtin, 2005) or decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation sensitivity and vocabulary is expected to grow considerably in the age range considered in the current meta-analysis (see wordbank.stanford.edu; Frank et al., 2017). The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary growth, as a facilitator for change in mispronunciation sensitivity. Yet, an analysis of correlations between vocabulary size and object recognition effect sizes does not support this argument. Although an increasing vocabulary size lead to increased object recognition for correctly pronounced words, this was not the case for mispronunciations. Some previous experimental evidence also supports a lack of a relationship between vocabulary size and mispronunciation sensitivity (e.g. Mani & Plunkett, 2007; Swingley & Aslin, 2000; but see Mani & Plunkett, 2010). This would suggest that object recognition for mispronunciations is not modulated by vocabulary size, contrary to the predictions of the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts and further supporting the overall lack of an influence of age on mispronunciation sensitivity.

@@

Although the lack of an relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis. Despite the theoretical implications, less than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total). We suggest that this may be the result of publication bias, specifically a desire to not publish null results. Although the number of mispronunciation sensitivity studies per year has seen an increase, this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.

@@

[Christina] It's a good start, let's see where we go from here. I jotted down some possible conclusions

## Data Analysis Choices

During data entry, we noted variation in how the different studies were analyzed, with the time window, offset from naming, and depending variable differing substantially in our sample. For the time window used for statistical analysis we find xxx

The lack of a field standard can have dire consequences, as our analyses show. Depending on which analysis time window (see figure xx) or dependent variable (see figure xx) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity. On one hand, this limits the conclusions we can draw. On the other hand, this finding emphasizes that current practices of free, seemingly ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.

We take this opportunity to suggest two remedies: Preregistration can serve as proof of a priori decisions regarding data analysis. The peer reviewed form of Registered Reports has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices. Open data can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.

[Christina: Are we submitting to a place with registered reports? We should!]

  + Post-naming time window size analyzed and dependent variable impact misp sensitivity measured
  + Offset time does not impact measurement of misp sensitivity 
  + the first two do not have theoretical frameworks to guide researchers, whereas offset time does

When it comes to designing studies, best practices and current standards might not always overlap. Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., 2018). A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework. Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere. We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation). Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.

## Limitations

@@

## Conclusion

First aggregation of studies

Advice for experiment design and design to be standardized, ideally preregistered.

Open science with anonymized data and more complex models might be the future, but without us noting the issues in the field, this cannot happen, so let's call for change now.
